Universal Anonymous Signatures

### 2022-10-06 prism-backend/research/gsac/app-related-proofs.tex
Minor edits.

We prove that our \CUASRing construction is anonymous and unforgeable, in the
model given in \cite{bkm06}, if the underlying $\CUASGen^{hide-iss}$
construction is secure.

\begin{theorem}[Anonymity of \CUASRing]
  If the base $\CUASGen^{hide-iss}$ construction is anonymous according to
  \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous ring signature
  scheme.
\end{theorem}

\begin{proof}
  Assume \adv~is an adversary against anonymity for \CUASRing.
  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
  generates $n$ key pairs for \adv~ simulating $KeyGen$ in \adv's game. Since
  $KeyGen$ simply uses algorithms of $\CUASGen^{hide-iss}$, \advB can do this
  directly via its own \HUGEN, \ISET, and \OGEN oracles, specifying
  $\fissue^{\sring}$ as issuance function, and $\finsp^0$ as opening function.
  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and answers
  \adv's \oracle{SIGN}(i,R,\msg) queries as follows. If user $i$ has not yet
  produced a credential for ring $R$, where $\pk_i \in R$, \advB makes a call to
  its \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
  produced, \advB simply reuses it. Then, \advB uses the corresponding user and
  credential identifiers as parameters to a query to its own \SIGN oracle
  (specifying $\feval^{\attrs}$ as signature evaluation function). Eventually,
  $\adv$ outputs two user indexes, a ring $R$, and message \msg. If the checks
  at lines 3-4 of \figref{fig:model-rs} pass, \advB generates the challenge
  signature by calling its own \CHALb oracle, and passes the result to $\adv$.
  Finally, \advB outputs whatever $\adv$ outputs.
  %
  The simulation of \adv's anonymity game is perfect, and \advB wins its game
  whenever \adv~ does.
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRing]
  If the base $\CUASGen^{hide-iss}$ construction is non-frameable according to
  \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
  scheme.
\end{theorem}

>>>>

We prove that our \CUASRing construction is anonymous and unforgeable, in the
model given in \cite{bkm06}, if the underlying \CUASGenHideIss
construction is secure.

\begin{theorem}[Anonymity of \CUASRing]
  If the base \CUASGenHideIss construction is anonymous according to
  \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous ring signature
  scheme.
\end{theorem}

\begin{proof}
  Assume \adv~is an adversary against anonymity for \CUASRing.
  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
  generates $n$ key pairs for \adv~ simulating $KeyGen$ in \adv's game. Since
  $KeyGen$ simply uses algorithms of \CUASGenHideIss, \advB can do this
  directly via its own \HUGEN, \ISET, and \OGEN oracles, specifying
  $\fissue^{\sring}$ as issuance function, and $\finsp^0$ as opening function.
  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and answers
  \adv's \oracle{SIGN}(i,R,\msg) queries as follows. If user $i$ has not yet
  produced a credential for ring $R$, where $\pk_i \in R$, \advB makes a call to
  its \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
  produced, \advB simply reuses it. Then, \advB uses the corresponding user and
  credential identifiers as parameters to a query to its own \SIGN oracle
  (specifying $\feval^{\attrs}$ as signature evaluation function). Eventually,
  $\adv$ outputs two user indexes, a ring $R$, and message \msg. If the checks
  at lines 3-4 of \figref{fig:model-rs} pass, \advB generates the challenge
  signature by calling its own \CHALb oracle, and passes the result to $\adv$.
  Finally, \advB outputs whatever $\adv$ outputs.
  %
  The simulation of \adv's anonymity game is perfect, and \advB wins its game
  whenever \adv~ does.
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRing]
  If the base \CUASGenHideIss construction is non-frameable according to
  \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
  scheme.
\end{theorem}
